\section{Conclusion}

Composable is on a mission to unlock the interconnected ecosystem of blockchains via a cross-chain, cross-layer networking fabric.
%
Moving assets intra-ecosystem is becoming more intuitive. However more and more applications have begun to shard operations across one or several blockchain L1 and L2 networks to minimize costs and maximise performance the implications being asset transfers and smart contract executions that are increasingly more complex and ambiguous. We are approaching a world in which the future of DeFi will be fully blockchain-agnostic.
%
Like Port Control Protocol of the Internet, Composable's mission is to service all these interactions, transfers, and communications cross-ecosystem.

Both developers and users will seek ways to interface with multiple ecosystems in a user-friendly, scalable, provable, and decentralized manner. In this construction paper, we discussed our thoughts and designs to provide this future in the form of Virtual Machines, Routing Layers, Finality and Application layers, and we introduced Mosaic the cross-ledger highly competitive transferal system backed by advanced engineering. All of our technologies are backed by strong guiding principles in both engineering and programming practices.

Composable's full technical stack is driving the evolution of digital assets and DeFi protocols. It enables the unification of functionality, across all blockchain ecosystems. We are engineering the fully interoperable future and we embrace the sharded efficient ecosystem which is rapidly expanding.
